DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2022-05-31 manuscript/manuscript.Rmd
adding table 2 to manuscript

_**Summarizing search results.-**_
DateLife obtained OpenTree's synthetic tree topology for these taxa (Fig. \ref{fig:figure2}C), and mapped age data to nodes in this chosen topology.
As expected, more inclusive nodes (e.g., node "n1") have more variance in age data than less inclusive nodes (e.g., node "n5").
The name processing step allowed including five data points for node "n4" (parent of _Schoeniclus elegans_; Fig. \ref{fig:figure2}A) that would not have had any data otherwise due to name mismatch.
Age summary statistics per node were calculated and used as calibrations to date the tree topology using the BLADJ algorithm.
Age data for node "n2" was excluded as final calibration because it is older than age data of the more inclusive node "n1" (Fig. \ref{fig:figure2}C4).

>>>>

_**Summarizing search results.-**_
DateLife obtained OpenTree's synthetic tree topology for these taxa (Fig. \ref{fig:figure2}C), and congruified and mapped age data to nodes in this chosen topology (Table \ref{tbl:table1}).
The name processing step allowed including five data points for node "n4" (parent of _Schoeniclus elegans_; Fig. \ref{fig:figure2}A) that would not have had any data otherwise due to name mismatch.
Age summary statistics per node were calculated (Table \ref{tbl:table2}) and used as calibrations to date the tree topology using the BLADJ algorithm.
As expected, more inclusive nodes (e.g., node "n1") have more variance in age data than less inclusive nodes (e.g., node "n5").
Summary age data for node "n2" were excluded as final calibration because they are older than age data of the more inclusive node, "n1" (Fig. \ref{fig:figure2}C4).

### 2022-05-31 manuscript/manuscript.tex
adding table 2 to manuscript

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Tree; Phylogeny; Scaling; Dating; Ages; Divergence times; Open Science; Congruification; Supertree; Calibrations; Secondary calibrations\newline\indent Word count: 4834}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\emph{\textbf{Summarizing search results.-}}
DateLife obtained OpenTree's synthetic tree topology for these taxa (Fig. \ref{fig:figure2}C), and mapped age data to nodes in this chosen topology.
As expected, more inclusive nodes (e.g., node ``n1'') have more variance in age data than less inclusive nodes (e.g., node ``n5'').
The name processing step allowed including five data points for node ``n4'' (parent of \emph{Schoeniclus elegans}; Fig. \ref{fig:figure2}A) that would not have had any data otherwise due to name mismatch.
Age summary statistics per node were calculated and used as calibrations to date the tree topology using the BLADJ algorithm.
Age data for node ``n2'' was excluded as final calibration because it is older than age data of the more inclusive node ``n1'' (Fig. \ref{fig:figure2}C4).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%    TABLE 1     %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \caption{Ages of congruified nodes belonging to step C3 from Figure3}
  \label{tbl:table1}
  \includegraphics[width=\linewidth]{../tables/table-fringillidae-small-example.pdf}
\end{table}

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Tree; Phylogeny; Scaling; Dating; Ages; Divergence times; Open Science; Congruification; Supertree; Calibrations; Secondary calibrations\newline\indent Word count: 4844}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\emph{\textbf{Summarizing search results.-}}
DateLife obtained OpenTree's synthetic tree topology for these taxa (Fig. \ref{fig:figure2}C), and congruified and mapped age data to nodes in this chosen topology (Table \ref{tbl:table1}).
The name processing step allowed including five data points for node ``n4'' (parent of \emph{Schoeniclus elegans}; Fig. \ref{fig:figure2}A) that would not have had any data otherwise due to name mismatch.
Age summary statistics per node were calculated (Table \ref{tbl:table2}) and used as calibrations to date the tree topology using the BLADJ algorithm.
As expected, more inclusive nodes (e.g., node ``n1'') have more variance in age data than less inclusive nodes (e.g., node ``n5'').
Age data for node ``n2'' was excluded as final calibration because it is older than age data of the more inclusive node ``n1'' (Fig. \ref{fig:figure2}C4).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%    TABLE 1     %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \caption{Ages of congruified nodes belonging to step C2 from Figure3}
  \label{tbl:table1}
  \includegraphics[width=\linewidth]{../tables/table-fringillidae-small-example.pdf}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%    TABLE 2     %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \caption{Summary of congruified nodes ages, corresponding to step C3 from Figure3}
  \label{tbl:table2}
  \includegraphics[width=\linewidth]{../tables/table-fringillidae-small-example-summary.png}
\end{table}
